How do school travel planning stakeholders frame active school travel in Ontario, Canada?

### 2021-11-26 AST-Framing-Ontario/AST-Framing-Ontario.Rmd

## 1.1. School travel planning in Canada

Walking and bicycling to school, commonly known as active school travel or active school transportation (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020]. This trend has prompted a multi-sector response to identify strategies to increase AST, the most popular of which is a growing interest in school travel planning across Canada.

School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health [@mammenSchoolTravelPlanning2014]. Parents and parent councils also typically have a role in supporting or implementing STP. The intervention encourages participation from the broader community and collaboration between involved stakeholders, who contribute their expertise to remove "school-specific" barriers to AST and to identify strategies for promoting and encouraging AST. STP may also involve other stakeholders including local advocacy groups or environmental organizations who are familiar with the state of AST at the community-level. Buliung et al. [-@buliungSchoolTravelPlanning2011] piloted an STP intervention at 12 schools in 4 Canadian provinces and reported that it increased AST rates and led to a "mobilization of diverse community resources". Since this seminal study, STP interventions have become increasingly popular and common at schools across Canada and have even attracted funding from provincial governments.

## 1.2. Correlates of active school travel

Factors that influence AST are typically conceptualized according to the socioecological model whereby children's travel behaviour is understood within the context of their household, social, and built environments [see @mitraIndependentMobilityMode2013]. At the individual level, older child age is often associated with AST [@mammenUnderstandingDriveEscort2012; @starkExploringIndependentActive2018; @wilsonUnderstandingChildParent2018]. There is some evidence that gender is a determinant of AST [@babbChildrenActiveTravel2017; @larsenInfluencePhysicalEnvironment2009], although this is not a strong or consistent finding [@rothmanDeclineActiveSchool2018; @schoeppeAssociationsChildrenActive2015]. Distance between home and school is associated with AST [@ikedaAssociationsChildrenActive2018; @mammenUnderstandingDriveEscort2012; @pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018] with less AST reported among children who have to travel farther to school. Car ownership is an important household-level influence on AST [@pontEnvironmentalCorrelatesChildren2009; @rothmanDeclineActiveSchool2018; @wilsonUnderstandingChildParent2018], as is household income [@pontEnvironmentalCorrelatesChildren2009]. Parental perceptions of the environment [@demeesterParentalPerceivedNeighborhood2014; @panterAttitudesSocialSupport2010] and children's skills [@ghekiereInsightsChildrenIndependent2017] also influence whether they allow their children to walk or cycle to school. Finally, many studies have found that the quality of the built environment [@ikedaAssociationsChildrenActive2018; @kimBuiltNaturalEnvironmental2020] and active travel infrastructure [@pontEnvironmentalCorrelatesChildren2009] facilitate AST. Concerns about traffic and strangers have been reported by parents who drive their children to school [@mammenUnderstandingDriveEscort2012]. The consensus is that all of these factors are interrelated and that interventions ought to target multiple factors in order to increase walking and bicycling levels to school.

## 1.3. Benefits of AST

The desire to increase AST is warranted - there is strong evidence that children who walk and bicycle to school accrue physical and mental health benefits. Many studies and reviews have focused on the association between AST or CIM and physical activity [e.g., @faulknerActiveSchoolTransport2009; @mitraChildrenActivitytransportationLifestyles2017; @schoeppeAssociationsChildrenActive2015], with findings consistently demonstrating that children who travel by walking or bicycling to school are more active than their peers who do not use active travel. More recently, researchers have been exploring the link between transport and children's wellbeing [@babbChildrenActiveTravel2017; @waygoodTransportChildrenWellbeing2020], which has relevant applications to the study of school travel and satisfaction [see @vandenbergFactorsAffectingParental2020]. CIM is also important for different domains of children's health and wellbeing [@riaziChildrenIndependentMobility2018]. It offers benefits such as increasing traffic and safety skills, boosting spatial awareness when navigating public spaces, and providing more opportunity for social interaction with peers [@schoeppeAssociationsChildrenIndependent2014].

## 1.4. Encouraging adoption of active school travel

To increase rates of walking and bicycling independently to school, Riazi et al. [-@riaziCorrelatesChildrenIndependent2019] state: "it will be vital for interventions to target modifiable factors, including children's and parents' perceptions of their social environment." Parents play the important role of "gatekeeper" by either granting or restricting CIM licenses, meaning whether children can travel alone [@sharminAssociationBuiltEnvironment2017]. For this reason, stakeholders involved in STP produce information targeted for both children and parents, and aim to involve the broader community in their efforts to increase the number of children walking and bicycling to school.

However, the ways in which interventions like STP are framed to their target audience can ultimately influence how they are received and whether they result in behaviour change. The correlates of AST are important knowledge for policymakers because they identify points of intervention and potential benefits that ought to be communicated to the public encourage adoption of AST and to build support for new planning paradigms. What is less clear is how CIM plays into the consideration of policymakers when they act on the objective of increasing AST.

Any goals for AST, and also CIM, ought to be clearly articulated and reflected in transportation plans and policies to guide initiatives. Presently, however, there has been no study to date that explores how Canadian municipalities and schools frame and discuss AST with the public. Content analysis is one method to analyze how particular issues are framed to groups of people, for instance parents or educators who might be inclined to support AST. It attempts to understand how information presented from a "communicator" leads the "receiver" to a desired response [@reynardGrowthResilienceHow2021]. In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review municipal policies addressing climate change in four western Canadian cities. Natural language processing (NLP) has also been used for a similar purpose to examine content in general plans from Californian cities [@brinkleyWhatPlanUsing2021]. The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.

## 1.5. Study aim

In 2017, the provincial government of Ontario in Canada issued funding to Green Communities Canada (GCC), a non-profit organization, to launch the _Ontario Active School Travel_ (OAST) program. The program provides funding for school and community-based initiatives and supports stakeholders in municipalities across the province to implement STP and other interventions aimed at increasing AST. As of 2021, OAST has funded _X_ projects in Ontario. GCC continues has funded projects across Ontario led by collaborative groups involving school boards, municipal or regional governments, and regional transportation consortia. The latter are dedicated transportation bodies that deliver efficient and effective transportation services, which generally focus on providing the school busing service to families in their associated region.

The aim of this paper is to analyze how AST is framed by STP stakeholders in Ontario, Canada. We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST. We compared the findings from these documents to a selection of studies on AST and explored the extent to which research findings have trickled down to inform policy and planning for increasing AST.

2. Data
===============

## 2.1. Data retrieval

### 2.1.1. Policy documents

We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public and English-speaking only); ii) municipal governments; and iii) transportation consortia. Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in initiatives.

The search was guided first by a list of all English public school boards across Ontario. The websites of each school board were manually searched for pages related to school transportation or travel. Any pages relevant to these topics were manually downloaded. Next, we collected documents by searching municipal government and transportation consortia websites. The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia who are in the same geographic area of each school board). Pages related to active or school travel were manually downloaded. Webpages from STP stakeholder websites were included in our analysis if they were easy to find. This primary criteria was important since our analysis pertains to how such issues are framed to the public. Thus, we included only webpages that were easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.

@@

### 2.2.1. Academic papers

## 2.2. Data cleaning

@@

3. Methods
===============

## 3.1. Natural language processing

## 3.2. Reproducibility

@@

4. Results
===============

## 4.1. Word and document frequency

@@

## 4.2. Bigrams and concordances

@@

```{r}
MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r}
ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r}
SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r}
PolicyTextDF <- data.frame(text = sapply(policy_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in all of the policy documents (i.e., school board, municipality, and transportation consortia combined."}
ggraph(policy_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "purple", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

We combined all of the municipality, school board, and transportation consortia documents into one "policy" corpora. This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario. Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the corpora. In addition to the common bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words. Overall, policy documents from STP stakeholders focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.

@@

```{r academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers."}
academic_bigrams_separated <- academic_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

```{r}
ggraph(academic_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

We interpreted the most common bigrams from the policy corpora (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholders are focusing on and communicating to the public about AST. We used the `kwic` function from the R _quanteda_ package to identify and better understand identify the context of these key themes.

@@

kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical", window = 10)
kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental", window = 10)
kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air", window = 10)
kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic", window = 10)
kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety", window = 10)
kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health", window = 10)
kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions", window = 10)
kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes", window = 10)
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone", window = 10)
kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus", window = 10)
kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community", window = 10)
kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit", window = 10)
kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather", window = 10)
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
```

```{r content-table, echo=FALSE}
text_tbl <- data.frame(
  Terms = c("Physical health", "Emissions"),
  Stakeholder = c("School Board", "Municipality"),
  Context = c(
    "ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.",
    "Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
)

@@

## 4.3. Topic modelling

```{r corpus-dtm, echo=FALSE}
# Create DTM from corpus

@@

```{r topics-number, echo=FALSE}
# Select number of topics for each LDA model using `ldatuning`

municipal_lda_num <- FindTopicsNumber(
  municipal_dtm, 
  topics = seq(from = 1, to = 10, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

school_lda_num <- FindTopicsNumber(
  school_dtm, 
  topics = seq(from = 1, to = 10, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

consortia_lda_num <- FindTopicsNumber(
  consortia_dtm, 
  topics = seq(from = 1, to = 10, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

policy_lda_num <- FindTopicsNumber(
  policy_dtm,
  topics = seq(from = 1, to = 10, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)
```

```{r topics-academic, echo=FALSE, cache=TRUE}
# DO NOT RUN EVERY TIME - takes approximately 20 minutes

#academic_lda_num <- FindTopicsNumber(
  #academic_dtm, 
  #topics = seq(from = 2, to = 50, by = 5),
  #metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  #method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE)
```

@@

FindTopicsNumber_plot(municipal_lda_num)
FindTopicsNumber_plot(school_lda_num)
FindTopicsNumber_plot(consortia_lda_num)
FindTopicsNumber_plot(policy_lda_num)
#(academic_lda_num)

# The graphs suggest that there are 7 topics for the municipal corpora
# The graphs suggest that there are 7 topics for the school corpora
# The graphs suggest that there are 5 topics for the municipal corpora
# The graphs suggest that there are 5 topics for the policy corpora
# The graphs suggest that there are 22 topics for the academic corpora
```

```{r corpus-lda-model, echo=FALSE}
municipal_lda <- LDA(municipal_dtm, k = 3, control=list(seed = 1, verbose = 25))

school_lda <- LDA(school_dtm, k = 3, control=list(seed = 1, verbose = 25))

consortia_lda <- LDA(consortia_dtm, k = 3, control=list(seed = 1, verbose = 25))

policy_lda <- LDA(policy_dtm, k = 3, control=list(seed = 1, verbose = 25))

#academic_lda <- LDA(academic_dtm, k = 22, control=list(seed = 1, verbose = 25))
```

```{r municipal-topics, echo=FALSE}
municipal_topics <- tidy(municipal_lda, matrix = "beta")
school_topics <- tidy(school_lda, matrix = "beta")
consortia_topics <- tidy(consortia_lda, matrix = "beta")
policy_topics <- tidy(policy_lda, matrix = "beta")
#academic_topics <- tidy(academic_lda, matrix = "beta")
```

@@

```{r academic-terms, echo=FALSE, cache=TRUE}
# Do not run; number of topics is not yet determined

#academic_top_terms <- academic_topics %>%
  #group_by(topic) %>%
  #slice_max(beta, n = 10) %>% 
  #ungroup() %>%
  #arrange(topic, -beta)

#academic_top_terms %>%
  #mutate(term = reorder_within(term, beta, topic)) %>%
  #ggplot(aes(beta, term, fill = factor(topic))) +
  #geom_col(show.legend = FALSE) +
  #facet_wrap(~ topic, scales = "free") +
  #scale_y_reordered()
```

```{r}
#municipal_beta <- municipal_topics %>%
  #mutate(topic = paste0("topic", topic)) %>%
  #pivot_wider(names_from = topic, values_from = beta) %>% 
  #filter(topic1 > .001 | topic2 > .001) %>%
  #mutate(log_ratio = log2(topic2 / topic1))
#municipal_beta
```

```{r document-matrix}
# Identify topics by document across each corpora

municipal_documents <- tidy(municipal_lda, matrix = "gamma")
school_documents <- tidy(school_lda, matrix = "gamma")
consortia_documents <- tidy(consortia_lda, matrix = "gamma")
policy_documents <- tidy(policy_lda, matrix = "gamma")
#academic_documents <- tidy(academic_lda, matrix = "gamma")
```

5. Discussion
===============

## 5.1. Implications for School Travel Planning

## 5.2. Limitations

6.1. Conclusion
===============

## 6.1. Future research

>>>>

Walking and bicycling to school, commonly known as active school travel (AST), has been declining in Canada and North America for decades [@rothmanDeclineActiveSchool2018], with levels much lower than other developed countries like The Netherlands [@vangoeverdenSchoolTravelBehaviour2013] and Japan [@waygoodChapterSixteenJapan2020]. In response to this trend, school travel planning has become a popular intervention across Canada that has resulted in mixed success with some schools reporting an increase in AST [e.g., @buliungSchoolTravelPlanning2011; @mammenActiveSchoolTravel2014], while others did not observe a change in behaviour [@buttazzoniPromotingActiveSchool2019] or needed more time and resources to be effective [@mammenPuttingSchoolTravel2015].

School travel planning (STP) is a "school-specific" intervention led by a facilitator that brings together a committee of stakeholders from diverse sectors including education, planning, transportation, and public health to develop action plans [@mammenSchoolTravelPlanning2014]. This five-step process involves identifying barriers to AST based on the local context and implementing approaches or activities that alleviate concerns and encourage AST [@faulknerSchoolTravelPlans2018]. STP facilitators and committee members generally intervene at the school through a range of activities such as educational strategies, in-person events or programs, improvements to the school site, and enforcement [@mammenActiveSchoolTravel2014].

How STP is framed to a target audience may influence how this intervention is received and whether it encourages the audience to support it or participate. In particular, STP stakeholders make choices about the points of intervention and potential benefits that ought to be communicated to the public to facilitate adoption of AST. Educational strategies, which account for approximately one quarter of STP strategies implemented at Canadian schools [@mammenActiveSchoolTravel2014], need to effectively engage multiple audiences – parents, students, politicians – on the issue, challenges, and benefits of AST. Promotional materials, therefore, should reflect current knowledge from research about school travel and the built environment, as well as local content specific to factors that influence travel decisions for parents, in order to effectively engage the public in advocating for improving AST or to expose parents and the community to essential information that may prompt behaviour change.

On the one hand, parents have been found to express different understandings, nomenclature, and conceptualizations than planners of the factors that influence school travel [@buliungLivingJourneySchool2021]. However, it is unknown to what degree there is concurrence between STP materials presented to the public and the literature on school travel and parental perceptions, and how the complexity of the AST issue is presented to the public.

The aim of this paper is to fill this research gap by analyzing how AST is framed by STP stakeholders in Ontario, Canada. We used text mining and topic modelling to examine how local policy documents from Ontario municipalities and school boards present and communicate the benefits and barriers of AST and the solutions for improving AST. We compared the findings from these documents to a selection of studies on AST and explored the extent to which there is concurrence between research findings to date and promotional materials shared with the public to increase AST.

2. Literature Review
======================

3. Data
===============

## 3.1. Data retrieval

### 3.1.1. Policy documents

We assembled a collection of publicly available documents that were sourced online from the main stakeholder groups involved in STP initiatives in Ontario: i) school boards (public and English-speaking only); ii) municipal governments; and iii) transportation consortia. Non-profit organizations, police services, and advocacy groups are other stakeholders who may play a role in supporting AST and/or STP, but this study does not include any documents from these groups because they are not consistently participating in all initiatives.

The search was guided first by a list of all English public school boards across Ontario. The websites of each school board were manually searched for pages related to school transportation or travel. Any pages relevant to these topics were manually downloaded. Next, we collected documents by searching municipal government and transportation consortia websites. The latter were identified based on geographic area (i.e., the municipalities and/or transportation consortia that are in the same geographic area of each school board). Pages related to active or school travel were manually downloaded. Webpages from STP stakeholder websites were included in our analysis if they were easy to find. This primary criteria was important since our analysis pertains to how such issues are framed to the public. Thus, we included only webpages that were easy to find, which we defined as requiring no more than 2-4 separate links from the initial Google search.

@@

### 3.2.1. Academic papers

__To be completed by Dr. Paez__

## 3.2. Data cleaning

@@

4. Methods
===============

## 4.1. Framing analysis

Issues that pertain to public health or wellbeing are often presented to the public through particular frames to influence perceptions or behaviours. Gamson and Modigliani [-@gamsonChangingCulture1987] conceptualize a frame as a “central organizing idea or story line that provides meaning” to a particular phenomenon. A frame can enable individuals "to locate, perceive, identify, and label" information pertaining to various dimensions of an issue [@goffmanFrameAnalysisEssay1974]. Scholars in the field of political communications have proposed that communicators, such as the media or an institution, construct the narrative of a frame for policy positions or public issues in order to activate or restrict a particular response in the intended audience [@panFramingAnalysisApproach1993]. Framing can be used to position existing solutions as suitable to address particular issues [@mahFramecriticalPolicyAnalysis2014], which may prevent the public from being aware of other policy approaches that challenge the status quo to bring about more radical change. The way policy issues are framed is ultimately important to understand because it plays a role in either altering or preserving the existing social perceptions.

Framing of issues is an important step in developing health policy. An obvious example over the past decade is the framing of climate change as a public health issue [e.g., @ depouxCommunicatingClimateChange2017; @maibachReframingClimateChange2010; @weathersDevelopmentsFramingClimate2016] to increase public engagement and reception of the issue. Transport planners also use different frames to guide the extent to which transport policies can be adapted to address climate change. In a recent paper [@reynardGrowthResilienceHow2021], framing analysis was applied to review the representation of issues such as mobility and social exclusion in municipal policies from four western Canadian cities under the current circumstances of climate change. The authors found four primary frames: “The Growing City”, “If You Build It, They Will Come”, “Better City for All”, and a “the Resilient City”. Each frame presented the nature, opportunities, and challenges of climate change in different ways which set the stage for the types of mitigation and adaptation strategies that cities were proposing to address this issue.

Given the range of factors at multiple levels of the socioecological model that influence school travel, it is important to understand how walking and bicycling to school are framed to the public. Is active school travel framed as a public health or environmental issue? Is it framed as both? Do proposed solutions to increase AST focus primarily on the intrapersonal and interpersonal factors, meaning that behaviour change must ultimately result from different decisions made by the individual or the household? Or is the decline in AST framed as an issue that must be addressed through changes in the built environment? These are the types of questions that we aim to answer in this paper. To our knowledge, this topic has not be addressed in the school travel literature to date.

## 4.2. Topic modelling

The topic modelling analysis was conducted in R. We primarily used the following packages: `topicmodels` [@R-topicmodels], `word2vec` [@R-word2vec], and `wordcloud` [@R-wordcloud] to examine content in the documents that were sourced for this project. These packages have functions for determining the frequency of specific words in each document, relationships (e.g., pairs of adjacent terms) and correlations between words, and estimating Latent Dirichlet allocation (LDA) models to classify documents according to the topics that are contained within them. We describe in the section below how we used these functions to produce our results.

## 4.3. Reproducibility

@@

5. Results
===============

## 5.1. Word and document frequency

@@

## 5.2. Bigrams and concordances

@@

```{r, include=FALSE}
MunicipalTextDF <- data.frame(text = sapply(municipal_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r, include=FALSE}
ConsortiumTextDF <- data.frame(text = sapply(consortium_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r, include=FALSE}
SchoolTextDF <- data.frame(text = sapply(school_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r, include=FALSE}
PolicyTextDF <- data.frame(text = sapply(policy_corpus, as.character), stringsAsFactors = FALSE)

@@

```{r policy-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found across all policy documents (i.e., school board, municipality, and transportation consortia combined)."}
ggraph(policy_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "purple", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

We then combined all municipality, school board, and transportation consortia documents into one "policy" corpora. This enabled us to examine and visualize the most common bigrams found across all of the STP material in Ontario that was collected for this study. Figure \ref{fig:policy-visual} shows all of the bigrams that occur more than 10 times in the corpora. In addition to the common bigrams already identified above, we also found _mental health_, _walk day_, and _green communities_ as common pairs of consecutive words. Overall, policy documents from STP stakeholders seem to focus on four key areas: i) benefits or impacts of AST; ii) mechanisms of intervention; iii) concerns or considerations; and iv) supports for AST.

@@

```{r, include=FALSE}
academic_bigrams_separated <- academic_bigrams %>%
  separate(bigram, c("word1", "word2"), sep = " ")

@@

```{r, academic-visual, echo=FALSE, fig.align = 'center', out.width = "100%", fig.cap = "Most common bigrams found in the academic papers.}
ggraph(academic_bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE,
                 arrow = a, end_cap = circle(.07, 'inches')) +
  geom_node_point(color = "lightgreen", size = 4) +
  geom_node_text(aes(label = name), repel = TRUE) + 
  theme_void()
```

We interpreted the most common bigrams from the policy corpora (see Figure \ref{fig:policy-visual}), which includes all documents from municipalities, transportation consortia, and school boards, as the main ideas that STP stakeholders are focusing on and communicating to the public about AST. We then used the `kwic` function from the R _quanteda_ package to identify and better understand the context of these key themes. Table \ref{tab:policy-concordance} presents examples of the key themes that were extracted from select policy documents to demonstrate how the most common bigrams are communicated to the public.

@@

kwic_pol_physical <- kwic(tokens(policy_quanteda), pattern = "physical", window = 10)
kwic_pol_mental <- kwic(tokens(policy_quanteda), pattern = "mental", window = 10)
kwic_pol_air <- kwic(tokens(policy_quanteda), pattern = "air", window = 10)
kwic_pol_traffic <- kwic(tokens(policy_quanteda), pattern = "traffic", window = 10)
kwic_pol_safety <- kwic(tokens(policy_quanteda), pattern = "safety", window = 10)
kwic_pol_health <- kwic(tokens(policy_quanteda), pattern = "health", window = 10)
kwic_pol_emissions <- kwic(tokens(policy_quanteda), pattern = "emissions", window = 10)
kwic_pol_routes <- kwic(tokens(policy_quanteda), pattern = "routes", window = 10)
kwic_pol_lanes <- kwic(tokens(policy_quanteda), pattern = "lanes", window = 10)
kwic_pol_zone <- kwic(tokens(policy_quanteda), pattern = "zone", window = 10)
kwic_pol_bus <- kwic(tokens(policy_quanteda), pattern = "bus", window = 10)
kwic_pol_comm <- kwic(tokens(policy_quanteda), pattern = "community", window = 10)
kwic_pol_ben <- kwic(tokens(policy_quanteda), pattern = "benefit", window = 10)
kwic_pol_wea <- kwic(tokens(policy_quanteda), pattern = "weather", window = 10)
```

```{r content-table, echo=FALSE}
text_tbl <- data.frame(
  Terms = c("Air Quality", "Benefit", "Bus", "Community", "Emissions", "Health", "Lanes", "Mental Health", "Physical Health"),
  Stakeholder = c("School Board", "Municipality", "School Board", "School Board", "Consortia", "Municipality", "Municipality", "Municipality", "Municipality"),
  Context = c(
    "Active transportation [...] improves air quality.",
    "Stronger bones and muscles, improved self-esteem and sense of well-being while reducing stress and risk of chronic disease all benefit those who use active transportation.",
    "While taking part in a walking school bus, your child will enjoy seeing friends on the way to school. They will be active more often. This is also a great opportunity for your child to socialize with school friends in a monitored and safe way where they can practice social distancing, modelled by a leader.",
    "Engage community stakeholders (school boards, municipalities, police, public health professionals, parents/guardians, administrators, educators and children) to work together to identify and to solve their school travel needs.",
    "An active school commute also reduces congestion in school zones and contributes to reducing greenhouse gas emissions – it’s a win-win for everyone!",
    "Active School Travel allows school-aged children the chance to participate in moderate to intense physical activity. This is linked with lower body mass index and improved cardiovascular health.",
    "We are continuing to build on the cycling and pedestrian network by adding more bike lanes, building multi-use paths and encouraging developments to provide better pedestrian/cycling environments.",
    "ASST not only improves physical and mental health but contributes to a healthier environment and safer streets.",
    "Encouraging Active Transportation promotes personal health and recreation, helps manage congestion, reduces emissions and supports municipal objectives for efficient land use.")
)

@@

## 5.3. Topic modelling

```{r corpus-dtm, include=FALSE}
# Create DTM from corpus

@@

```{r topics-number, include=FALSE}
# Select number of topics for each LDA model using `ldatuning`

municipal_lda_num <- FindTopicsNumber(
  municipal_dtm, 
  topics = seq(from = 2, to = 15, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

school_lda_num <- FindTopicsNumber(
  school_dtm, 
  topics = seq(from = 2, to = 15, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

consortia_lda_num <- FindTopicsNumber(
  consortia_dtm, 
  topics = seq(from = 2, to = 15, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)

policy_lda_num <- FindTopicsNumber(
  policy_dtm,
  topics = seq(from = 2, to = 15, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE
)
```

```{r topics-academic, include=FALSE, cache=TRUE}
# DO NOT RUN EVERY TIME - takes approximately 20 minutes

academic_lda_num <- FindTopicsNumber(
  academic_dtm, 
  topics = seq(from = 2, to = 25, by = 1),
  metrics = c("Griffiths2004", "CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs")
  #control = list(seed = 77),
  #mc.cores = 2L,
  #verbose = TRUE)
```

@@

FindTopicsNumber_plot(municipal_lda_num)
FindTopicsNumber_plot(school_lda_num)
FindTopicsNumber_plot(consortia_lda_num)
FindTopicsNumber_plot(policy_lda_num)
FindTopicsNumber_plot(academic_lda_num)

# The graphs suggest that there are 4 topics for the municipal corpora
# The graphs suggest that there are 4 topics for the school corpora
# The graphs suggest that there are 4 topics for the municipal corpora
# The graphs suggest that there are 5 topics for the policy corpora
# The graphs suggest that there are 17 topics for the academic corpora
```

```{r corpus-lda-model, include=FALSE}
municipal_lda <- LDA(municipal_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)

school_lda <- LDA(school_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)

consortia_lda <- LDA(consortia_dtm, k = 4, method = "Gibbs", control = NULL, model = NULL)

policy_lda <- LDA(policy_dtm, k = 5, method = "Gibbs", control = NULL, model = NULL)

academic_lda <- LDA(academic_dtm, k = 19, method = "Gibbs", control = NULL, model = NULL)
```

```{r municipal-topics, include=FALSE}
municipal_topics <- tidy(municipal_lda, matrix = "beta")
school_topics <- tidy(school_lda, matrix = "beta")
consortia_topics <- tidy(consortia_lda, matrix = "beta")
policy_topics <- tidy(policy_lda, matrix = "beta")
academic_topics <- tidy(academic_lda, matrix = "beta")
```

@@

```{r academic-terms, echo=FALSE, cache=TRUE}

academic_top_terms <- academic_topics %>%
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)

academic_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()
```

Finally, we conducted topic modelling to examine the different topics found in the policy and academic corpora. We focused on the policy corpora, instead of individually assessing the municipal, school, and consortia corpus, so that we could report on the primary and secondary frames used across all documents put out by STP stakeholders in Ontario. To determine the number of discrete topics in each corpus, we used the ldatuning package. We then used the `LDA` function from the topicmodels package to estimate an LDA model for each group of documents. The policy corpora, which combined all documents from municipalities, schools, and transportation consortia, had 5 topics. The academic corpora had 17 topics. Figures \ref{fig: policy-terms} and \ref{fig: academic-terms} present the main terms that are associated with the topics found in each corpus.

In the policy corpus, we identified the following topics: (1) resources for walking, (2) busing information and eligibility; (3) benefits of active travel; (4) bicycling and the environment; and (5) supporting active travel. These findings reveal that STP stakeholders are sending the message that walking and bicycling to school as healthy travel modes for students, particularly as a means to get physical activity. We also found that there is information shared to support parents and students in using active modes to school such as the availability of cycling lanes or route tips for walking. STP stakeholders appear to be communicating that AST is possible and safe as a result of improvements to the built environment and available resources for parents and children. A final focus in the policy documents is on various efforts that are underway to support active travel including route planning.

We expected to find a higher number of topics in the academic corpus due to the larger number of documents in the corpora and the diversity of content examined in existing literature about school travel. The following topics were identified, which touch upon a broader range of factors that are associated with or related to AST than are found in the policy corpus: (1) __unclear__ (2) AST in Ontario and Canada; (3) __unclear__; (4) children’s independent mobility; (5) safe routes to school programs; (6) commuting and distance; (7) density in the built environment and walking routes; (8) __unclear__; (9) walking interventions; (10) bicycling influences; (11) interpersonal and household influences on trips; (12) behaviours and attitudes; (13) __unclear__; (14) __unclear__; (15) walking distance; (16) __unclear__;  (17) physical activity measures or results; (18) bicycling attitudes; and (19) __unclear__.
